### 2023-02-14 Documentation/UFMG/Relatorio_4/Development/Development.tex
documentation

>>>>

\subsection*{2.1 Mapping experiments}

    \begin{figure}[H]
        \center
        \includegraphics[width=10cm]{images/image_folder_report_4/manualMap1.png}
        \caption{Control model implemented in software}
    \end{figure}

    \begin{figure}[H]
        \center
        \includegraphics[width=10cm]{images/image_folder_report_4/manualMap2.png}
        \caption{Control model implemented in software}
    \end{figure}

    \begin{figure}[H]
        \center
        \includegraphics[width=10cm]{images/image_folder_report_4/manualMap3.png}
        \caption{Control model implemented in software}
    \end{figure}

    \begin{figure}[H]
        \center
        \includegraphics[width=15cm]{images/image_folder_report_4/mapXman-1.png}
        \caption{Control model implemented in software}
    \end{figure}

    \begin{figure}[H]
        \center
        \includegraphics[width=15cm]{images/image_folder_report_4/mapXman-2.png}
        \caption{Control model implemented in software}
    \end{figure}
